---
title: "SSVEP_Faces"
author: "Richard"
date: "1 March 2016"
output: pdf_document
---

```{r setup, echo=FALSE, warning=FALSE}
setwd("~/Dropbox/PhD/Study_16_SSVEP/Data")
library(ggplot2)
library(knitr)
library(gdata)
library(Rmisc)
require(reshape2)
ssvep <- read.xls("TempData.xlsx")
opts_chunk$set(echo = FALSE, cache=FALSE)
read_chunk('~/Dropbox/PhD/Study_16_SSVEP/Scripts/remove_outliers.R')
```

Remove outliers
```{r, echo=FALSE, warning=FALSE}
<<remove-outliers>>
#ssvep$outAQ <- remove_outliers(ssvep$AQ.sum)
#ssvep$outSNR1 <- remove_outliers(ssvep$fnr_2.4)
#ssvep$outSNR2 <- remove_outliers(ssvep$fnr_6.0)
#ssvep$outFFA1 <- remove_outliers(ssvep$X6hz.amp)
#ssvep$outFFA2 <- remove_outliers(ssvep$X2.4hz.amp)
new_ssvep <- ssvep[complete.cases(ssvep),]
```



Plots
```{r, echo=FALSE}
myList1 <- list(ssvep$AQ.sum,new_ssvep$AQ.sum)
df1 <- melt(myList1)
df1$L1 <- as.factor(df1$L1)
ggplot(data = df1, aes(x = L1, y = value)) +
     geom_boxplot(aes(group = L1,fill=L1)) +
     theme(legend.position="none") +
     ylab("AQ")

myList2 <- list(ssvep$X2.4hz.amp,new_ssvep$X2.4hz.amp)
df2 <- melt(myList2)
df2$L1 <- as.factor(df2$L1)
ggplot(data = df2, aes(x = L1, y = value)) +
     geom_boxplot(aes(group = L1,fill=L1)) +
    theme(legend.position="none") +
ylab("ffa amplitude 2.4Hz")

myList3 <- list(ssvep$X6hz.amp,new_ssvep$X6hz.amp)
df3 <- melt(myList3)
df3$L1 <- as.factor(df3$L1)
ggplot(data = df3, aes(x = L1, y = value)) +
     geom_boxplot(aes(group = L1,fill=L1)) +
    theme(legend.position="none") +
ylab("ffa amplitude 6Hz")

myList4 <- list(ssvep$X2.4hz.snr,new_ssvep$X2.4hz.snr)
df4 <- melt(myList4)
df4$L1 <- as.factor(df4$L1)
ggplot(data = df4, aes(x = L1, y = value)) +
     geom_boxplot(aes(group = L1,fill=L1)) +
    theme(legend.position="none") +
ylab("SNR at 2.4Hz")

myList5 <- list(ssvep$X6hz.snr,new_ssvep$X6hz.snr)
df5 <- melt(myList5)
df5$L1 <- as.factor(df5$L1)
ggplot(data = df5, aes(x = L1, y = value)) +
     geom_boxplot(aes(group = L1,fill=L1)) +
    theme(legend.position="none") +
ylab("SNR at 6Hz")
```


Pearson Correlation & plot

```{r, echo=FALSE, warning=FALSE, results="hide"}
# get the correlation
High <- cor.test(new_ssvep$AQ.sum, new_ssvep$X6hz.amp, method = "pearson")

# plot the correlation
ggplot(new_ssvep, aes(x=new_ssvep$X6hz.amp, y=new_ssvep$AQ.sum)) + geom_point(shape=1) + scale_colour_hue(l=50) + # Use brewermap
  geom_smooth(method=lm,   # Add linear regression lines
              se=TRUE,    # Don't add shaded confidence region
              fullrange=TRUE) + ggtitle("SSVEP") + xlab("SSVEP Response 6Hz") + ylab("Autism Quotient")
```

The estimated correlation between AQ and SSVEP at 6Hz is `r cor(new_ssvep$AQ.sum, new_ssvep$X6hz.amp)` with an estimated p-value of `r High$p.value`.

```{r, echo=FALSE, warning=FALSE, results="hide"}
# get the correlation
Low <- cor.test(new_ssvep$AQ.sum, new_ssvep$X2.4hz.amp, method = "pearson")

# plot the correlation
ggplot(new_ssvep, aes(x=new_ssvep$X2.4hz.amp, y=new_ssvep$AQ.sum)) + geom_point(shape=1) + scale_colour_hue(l=50) + # Use brewermap
  geom_smooth(method=lm,   # Add linear regression lines
              se=TRUE,    # Don't add shaded confidence region
              fullrange=TRUE) + ggtitle("SSVEP") + xlab("SSVEP Response 2.4Hz") + ylab("Autism Quotient")
```

The estimated correlation between AQ and SSVEP at 2.4Hz is `r cor(new_ssvep$AQ.sum, new_ssvep$X2.4hz.amp)` with an estimated p-value of `r Low$p.value`.

```{r, echo=FALSE, warning=FALSE, results="hide"}
# get the correlation
Ratio <- cor.test(new_ssvep$AQ.sum, new_ssvep$Ratio, method = "pearson")

# plot the correlation
ggplot(new_ssvep, aes(x=new_ssvep$Ratio, y=new_ssvep$AQ.sum)) + geom_point(shape=1) + scale_colour_hue(l=50) + # Use brewermap
  geom_smooth(method=lm,   # Add linear regression lines
              se=TRUE,    # Don't add shaded confidence region
              fullrange=TRUE) + ggtitle("SSVEP") + xlab("SSVEP Response Ratio") + ylab("Autism Quotient")
```

The estimated correlation between AQ and SSVEP Ratio is `r cor(new_ssvep$AQ.sum, new_ssvep$Ratio)` with an estimated p-value of `r Ratio$p.value`.
